Cudele: A File System with Programmable Consistency and Durability

### 2017-03-23 paper/sections/3_posix_overheads.tex
paper: edit section 3
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\begin{figure}[tb]
\centering
\includegraphics[width=75mm]{figures/creates-motivation.png}
\caption{Create-heavy workloads (untar) incurr the highest disk, network, and CPU
utilization because the metadata server is managing consistency and fault
tolerance.}\label{fig:creates-motivation}
\end{figure}

In our examiniation of the overheads of POSIX we benchmark and analyze CephFS,
the file system that uses the RADOS object store to store its data and
metadata. We choose CephFS because it is an open-source production quality
system. CephFS made one set of design decisions and we not asserting that the
design decisions that were made are superior but instead highlight the
effect those decisions have on performance.

>>>>

\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{figures/creates-motivation.png}
\caption{Create-heavy workloads (untar) incurr the highest disk, network, and CPU
utilization because the metadata server is managing consistency and fault
tolerance.}\label{fig:creates-motivation}
\end{figure}

In our examiniation of the overheads of POSIX we benchmark and analyze CephFS,
the file system that uses the Ceph's object store ({\it i.e.} RADOS) to store
its data and metadata. We choose CephFS because it is an open-source production
quality system. This file system is an implementation of one set of design
decisions; we are not asserting that those decisions are superior but instead
highlight the effect that those decisions have on performance.

### 2017-03-23 paper/sections/6_results.tex
paper: edit section 3
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

@@

\begin{figure}[tb]
\centering
\includegraphics[width=75mm]{graphs/slowdown-mechanisms.png}
\caption{}
\end{figure}
\begin{figure}[tb]
\centering
\includegraphics[width=75mm]{graphs/slowdown-related-work.png}
\caption{}
\end{figure}
\begin{figure}[tb]
\centering
\includegraphics[width=75mm]{graphs/slowdown-strong-v-eventual.png}
\caption{}
\end{figure}

>>>>

We evaluate Cudele on a 15 node cluster, partitioned into 8 object storage
servers, 3 metadata servers, and 2 monitor servers. The object storage servers
double as clients which is fine because clients are CPU and memory bound while
object storage servers are disk IO bound. All daemons run as a single process
which is the default setting for Ceph and the nodes have 2 dual core 2GHz
processors with 8GB of RAM. There are three daemons per object storage server
(one for each disk formatted with XFS) and they share an SSD for the journal.
The nodes are running Ubuntu 12.04.4, kernel version 3.2.0-63 but all
experiments run in Docker containers; this makes it easier to tear down and
re-initialize ({\it e.g.}, dropping the kernel cache) for the cluster between
experiments.

This paper adheres to The Popper
Convention\footnote{\url{http://falsifiable.us}}~\cite{jimenez_popper_2016}, so
experiments presented here are available in the repository for this
article\footnote{\url{https://github.com/michaelsevilla/cudele-popper/tree/}}.
Experiments can be examined in more detail, or even re-run, by visiting the
\texttt{[source]} link next to each figure. That link points to a Jupyter
notebook that shows the analysis and source code for that graph and its parent
folder contains all the associated artifacts.

@@

\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/slowdown-mechanisms.png}
\caption{}
\end{figure}
\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/slowdown-related-work.png}
\caption{}
\end{figure}
\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/slowdown-strong-v-eventual.png}
\caption{}
\end{figure}
